\LARGE \bf Efficient Planar Sample-Based Grasp Planning with Uncertainty Using Budgeted Multi-Armed Bandit Models for [v3 Jan 5, 2015 ]

### 2015-01-10 paper.tex
Revised sections 1-5. Still needs a number of revisions, particularly in section 5.

\usepackage{tikz,hyperref,graphicx,units,subfig}
\usepackage{subfig}
\usepackage{benktools}
\usepackage{caption}
\renewcommand{\captionfont}{\footnotesize}
\usepackage{sidecap,wrapfig}
\usepackage[ruled,vlined]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\abs}[1]{\lvert#1\rvert} 
\newcommand{\norm}[1]{\lVert#1\rVert}
%\newcommand{\suchthat}{\mid}
\newcommand{\suchthat}{\ \big|\ }
\newcommand{\bd}{\mathbf{d}}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bt}{\mathbf{t}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\bbf}{\mathbf{f}}
\newcommand{\bzero}{\mathbf{0}}
\newcommand{\bG}{\mathbf{G}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\bW}{\mathbf{W}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\mX}{\mathcal{X}}
\newcommand{\mD}{\mathcal{D}}
\newcommand{\mN}{\mathcal{N}}
\newcommand{\mW}{\mathcal{W}}
\newcommand{\mF}{\mathcal{F}}
\newcommand{\bZ}{\mathbf{Z}}

@@

\begin{abstract}
\textit{Abstract---}\todo{Not sure if we need to change the authors list or not}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.  Monte-Carlo sampling is computationally demanding, even for planar models. We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.  We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.  To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object with shape uncertainty defined by a Gaussian process implicit surface (GPIS), but the method is also applicable to other models of uncertainty.  We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.  This suggests a number of new research questions about how MAB can be applied to other models of uncertainty and how different MAB solution techniques can be applied to further reduce computation.
\end{abstract}

\begin{abstract}
\textit{Note to Practitioners---}Planning for a grasp in an unknown environment can be difficult due to uncertainties. For example, a given object may have transparency which makes modern kinect-like sensor unable to accurately determine shape or an object may have a built up of mildew or dust, which makes the friction coefficient unknown. To handle all the uncertainties and plan for grasps using a grasp metric, one must perform monte-carlo integration and exhaustively evaluate samples. We show that by using simple algorithms from the Multi-Armed bandit literature, you can intelligently decided which grasp to sample from next and quickly determine the best grasp in a given set of proposed grasps, thus helping to alleviate the computational burden that is associated to incorporating uncertainty. 
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Consider a robot processing orders in a warehouse , where it frequently encounter new consumer products and need to process them quickly.
The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape, pose and material properties like friction coefficient or center of mass. 
Furthermore, the robot may not be able to measure these quantities exactly due to sensor noise and missing data resulting from occlusions and object properties such as transparency or reflective surfaces .

\begin{figure}%
    \centering
     \subfloat{{\includegraphics[width=8cm]{figures/cup.jpg} }}%

       \qquad

@@

Grasp quality metrics have been developed to determine if a grasp will be successful or not prior to actually executing the grasp and how much force it needs to exert to resist an opposing force, however the ones that we consider evaluate a grasp assuming all the parameters are known \cite{ferrari1992}.
Recent work \cite{kehoe2012estimating,mahler2015gp} motivated using knowledge of uncertainty to select grasps, but most methods for evaluating grasp quality in the presence of uncertainty use Monte Carlo sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.

To select a grasp with high quality this evaluation is usually performed for a large set of perturbations in state, shape, and material properties, which can be very time-consuming.
However, when evaluating a set of grasps we may be able to determine the difference of quality between proposed grasps with only a few samples and adaptively choose what grasp to evaluate next. We can concentrate grasp quality evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.

The multi-armed bandit (MAB) model for sequential decision making problems \cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a way to reason about selecting the next option to evaluate.
The goal in a MAB model is to make a sequence of decisions over a set of possible options, or ``arms", such that a measure of expected reward is maximized.
Solutions to the MAB model are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model where at a given "stopping time" the agent must choose the arm that currently has the highest expected reward based on its observations. 
The objective is to maximize the expected reward of the decision made at the stopping time, or equivalently to minimize ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.

Our main contribution is formulating the problem of planning grasps according to some quality metric in the presence of uncertainty as a budgeted multi-armed bandit model.
We use this formulation to rank a set of potential grasps by the probability of force closure \cite{christopoulos2007handling, kehoe2012toward} under uncertainty in pose, shape, motion and friction coefficient. 
We choose the model of shape uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}.  Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object. Uncertainity in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.  Our approach of treating grasp selection as a BMAB requires only the ability to sample from a given representation of uncertainty and is not restricted to aforementioned representations.

We also show how to estimate distributions on the contact points and surface normals and center of mass using GPIS representation for shape uncertainty. Our experiments demonstrate that using the MAB sampling method improves the time to find the best grasp in a set of 1000 grasps by 5x over the baseline Monte-Carlo approach. 
\todo{Going to get a table with results}

@@

Past work on grasping under uncertainty has considered shape uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
The effect of uncertainty in object geometry on grasp selection has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.

One method of evaluating the expected grasp quality under uncertainty is to rank a set of random grasps on an object using  samples on shapes, pose or parameters to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.

To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of samples needed in Monte-Carlo sampling to choose the highest quality grasps. However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is, which in practice could lead to good grasps being thrown away.
Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty when the robot is able to obtain new information via tactile sensor.
MCMC provides a Bayesian framework for inference with a hidden state, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.

@@

\section{Preliminaries and Problem Definition}
Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action. We also introduce a graphical model to represent the distributions on friction coefficient, motion, pose and shape.

\subsection{Grasp Metric}
Ferrari and Canny \cite{ferrari1992} demonstrated a method to rank grasps by considering points of contact with an object and the object surface normals at those contacts. The magnitude of the metric allows one to rank grasps by their ability to resist external wrenches (forces and torques) applied to the grasped object. The Ferrari-Canny metric has wide spread use in grasp packages like GraspIT\cite{miller2004graspit}, OpenGrasp\cite{73} and Simox \cite{vahrenkamp2010simo}, which motivates studying its effect with uncertainties.

Let Q be the $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$. The metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. If the convex hull  encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used. A grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$\cite{pokorny2013classical}.

In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps . $P(Q>0)$ may be computed by sampling from distributions on pose (rotation and translation of the object), shape and material properties (friction coefficient) and averaging the qualities that are computed.

\subsection{Line of action}
In an uncertain environment, a grasp planner may not know the true grasp parameters or $g$ exactly due to sensing imprecision. Thus we propose to work with the trajectory of the gripper when analyzing grasps. Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.

\begin{figure}[ht!]
\centering
\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
\vspace*{-10pt}
\label{fig:line_of_action}
\end{figure}

\subsection{Types of Uncertainty}
In this work we consider the following types of uncertainty shape, pose, movement, and friction coefficient.  The property of force closure is not affected by the center of mass because it  measures if a wrench can be resisted not how large the force is need to resist.  Fig. \ref{fig:graphical_model} shows the probabilistic relationship of the types of uncertainty considered in this work. We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle the types of uncertainty. We note though that our choice of distributions does not effect the ability to use the MAB algorithms and that the reader should choose distribution that effect their needs.

\subsubsection{Distribution on Shape}

Shape uncertainty can occur from transparency, occlusions and sensor noise \cite{mahler}. To model this uncertainty we use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Appendix \ref{sec:Appendix}.  A GPIS is a Gaussian distribution on a signed distance function,$sd$, that describes the workspace. A signed distance function is  greater than 0 outside the surface of an object, 0 at the surface and less than 0 beneath.  Signed distance functions can be sampled from  $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS. For our application, we set $x$ to discretized points along the workspace $\mathcal{W}$ and for each sample the points that correspond to zero, $sd(x) = 0$, are the contours of the shape. For convenience we will  represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.

\subsubsection{Distribution on Pose}
In typical robotics applications the pose of objects in the envinroment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
Therefore pose uncertainty may come from two primary sources a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
The effects of pose uncertainty on robotic grasping has been studied by ~\cite{}.

The pose of an object $T$ is a member of the Lie Algebra $SE(3)$ in 3-dimensional space (something analogous holds for 2D).
This matrix is defined by 3 rotation angles $\bw = (\alpha, \beta, \gamma)$ and 3 translation coordinates $\bt = (t_x, t_y, t_z)$, summarized in parameter vector $\mathbf{\xi} = (\bw, \bt)^T \in \mathbb{R}^6$.
One challenge with pose is that uncertainty in the pose matrix $T$ used to apply transformations is needed in practice, but uncertainty is mathematically more easily to quantify in terms of the pose parameters $\xi$.
Thus given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma \right)$ we define the pose random variable $T$ as

@@

\noindent where the $\wedge$ operator is defined as in \cite{barfoot2014Pose}.

 \subsubsection{Distribution on Motion}
 In practice a robot may not be able to execute a desired
grasp plan $\Gamma$ exactly due to errors in trajectory following or
registration to the object \cite{kehoe2012estimating}. To handle this uncertainity, we sample the angle of approach $\rho$ of the proposed grasp plan $\Gamma$ from a zero mean one-dimensional Guassian $\rho \sim N(0,\sigma_{mot}^2)$. In practice $\sigma_{mot}^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.

 \subsubsection{Distribution on Friction Coefficient}
As shown in \cite{zheng2005}, uncertainty in friction coefficient can play a large role in grasp quality evaluation. The expected friction coefficient $E(\mu)$ can be derived by means of object classification and a look up table. However, because their could be material in between the objects surface and the robot gripper (i.e. dust, water, moisture), we purpose sampling the friction coefficient from a Gaussian around the expected friction coefficient $\mu \sim N(E(\mu),\sigma_{\mu}^2)$.

To estimate $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig. \ref{fig:graphical_model}. To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$. Using Bayes rule  we can rewrite this as

>>>>

\usepackage{tikz,hyperref,graphicx,units,subfig}
\usepackage{subfig}
\usepackage{benktools}
\usepackage{caption}
\renewcommand{\captionfont}{\footnotesize}
\usepackage{sidecap,wrapfig}
\usepackage[ruled,vlined]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\abs}[1]{\lvert#1\rvert} 
\newcommand{\norm}[1]{\lVert#1\rVert}
%\newcommand{\suchthat}{\mid}
\newcommand{\suchthat}{\ \big|\ }
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bb}{\mathbf{b}}
\newcommand{\bc}{\mathbf{c}}
\newcommand{\bd}{\mathbf{d}}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bt}{\mathbf{t}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\bbf}{\mathbf{f}}
\newcommand{\bzero}{\mathbf{0}}
\newcommand{\bG}{\mathbf{G}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\bW}{\mathbf{W}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\mX}{\mathcal{X}}
\newcommand{\mD}{\mathcal{D}}
\newcommand{\mG}{\mathcal{G}}
\newcommand{\mN}{\mathcal{N}}
\newcommand{\mW}{\mathcal{W}}
\newcommand{\mF}{\mathcal{F}}
\newcommand{\bZ}{\mathbf{Z}}

@@

\begin{abstract}
\textit{Abstract---}\todo{Not sure if we need to change the authors list or not}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.  Monte-Carlo sampling is computationally demanding, even for planar models. We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.  We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.  To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object with shape uncertainty defined by a Gaussian process implicit surface (GPIS), but the method is also applicable to other models of uncertainty.  We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.
\end{abstract}

\begin{abstract}
\textit{Note to Practitioners---}Planning for a grasp in an unknown environment can be difficult due to uncertainties. For example, a given object may have transparency which makes modern kinect-like sensor unable to accurately determine shape or an object may have a built up of mildew or dust, which makes the friction coefficient unknown. Monte-Carlo integration is often used to exhaustively evaluate the distribution on a grasp quality metric given these uncertainties. We apply algorithms from the sequential decision making literature to intelligently allocate samples for grasp quality evaluation to grasps likely to have higher quality given the previous samples, reducing plan time by roughly an order of magnitude.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Consider a robot processing orders in a warehouse, where it frequently encounters new consumer products and must process them quickly.
The robot may need to rapidly plan grasps for these objects without prior knowledge of object shape, pose and material properties like friction coefficient or center of mass. 
Furthermore, the robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which may result from occlusions or surface properties such as transparency or reflective surfaces.

\begin{figure}%
    \centering
%     \subfloat{{\includegraphics[width=8cm]{figures/cup.jpg} }}%

%       \qquad

@@

Analytic grasp quality metrics have been developed to determine the stability of a grasp when all the parameters of the object and robot manipulator are exactly known.
A common measure of stabliity in the literature is force closure, the abliity to resist external forces and torques in arbitrary directions~\cite{}.
Grasps in force closure can be further ranked by the relative magnitude of forces and torques that must be exterted by the gripper to resist external perturbations~\cite{ferrari1992}.
Recent works have explored computing the probability of a grasp achieving the force closure condition given uncertainty in parameters such as pose~\cite{christopoulos2007handling, weisz2012pose, kim2012physically} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
Most methods for evaluating grasp quality in the presence of uncertainty use exhaustive Monte-Carlo sampling over the possible values of uncertain quantities~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards} which can be very time consuming..
However, in many cases we may be able to rule out grasps with a low probability in only a few samples and allocate more sampling effort to grasps that are likely to be high quality.

The multi-armed bandit (MAB) model for sequential decision making problems~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a formal way to reason about allocating sampling effort to grasps such that the grasp(s) with highest quality can be determined in as few samples as possible.
In a standard MAB there are a set of possible options (or `arms' in the literature~\cite{barto1998reinforcement}) that each return a numeric reward from a stationary distribution.
The goal in a MAB problem is to sequentially select ones of the possible options such that a measure of expected reward is maximized.
Solutions to the MAB model are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model where an agent has a fixed number of decisions to make before choosing the best option.
The objective is to maximize the expected reward of the decision made at the stopping time, or equivalently to minimize ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.

Our main contribution is formulating the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a budgeted multi-armed bandit problem. %\todo{Jeff: probably needs to be more specific here, unless we formally describe how to do it in an arbitrary model}.
We study this formulation using probability of force closure~\cite{christopoulos2007handling, weisz2012pose, kehoe2012toward} as a quality metric under uncertainty in pose, shape, robot motion, and friction coefficient. 
We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}. 
Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object.
Uncertainity in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
\todo{Jeff: I personally think the above 3 statements may be too much detail for an intro}
However, our approach of treating grasp selection as a BMAB only requires the ability to sample from a given representation of uncertainty and is not restricted to aforementioned representations.
We compare the performance of several popular algorithms for solving the BMAB problem: Bayes UCB, Thompson sampling, and Gittins indices.
Our experiments demonstrate that solutions to the MAB problem can find the grasp with highest probabilty of force closure from a set of 1000 grasps 5x faster than the baseline Monte-Carlo approach and ...
\todo{Going to get a table with results. Make comparison to Ben's method}

@@

Past work on grasping under uncertainty has considered shape uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, and uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
The effect of uncertainty in object geometry on grasp selection has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.
A common method for evaluating a probabilistic grasp quality measure is to use Monte-Carlo sampling~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}, which involves exhaustively sampling from distributions on random quantities and averaging the quality over these samples to approximate an expected value~\cite{caflisch1998monte}.
Exhaustive sampling can be computationally expensive, which motivated the use of Cloud Computing to distribute sampling effort~\cite{kehoe2012toward}.

To further address the computational complexity, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of samples needed in Monte-Carlo sampling to choose the highest quality grasps. However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is, which in practice could lead to good grasps being thrown away.
Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty when the robot is able to obtain new information via tactile sensor.
MCMC provides a Bayesian framework for inference with a hidden state, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.

@@

\section{Preliminaries and Problem Definition}
We consider selecting a grasp on object from a given set of candidate grasps.
We formulate this problem for grasping a planar object from above using parallel-jaw grippers.
We assume that the object is rigid and remains stationary throughout the grasp.
In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient and we assume that distributions on these quantiites are given.
In this section, we formally define our grasping model, formalize our sources of uncertainty, introduce our metric for grasp quality, and finally define our grasp planning objective.

%Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action. We also introduce a graphical model to represent the distributions on friction coefficient, motion, pose and shape.

\subsection{Candidate Grasp Model}
Our candidate grasp model is illustrated in Fig.~\ref{fig:grasp_model}.
Let $d$ denote the dimensionality of the shape representations we are using to select grasps and $m$ denote the number of jaws on the robotic gripper.
In this work we formulate the MAB problem for 2-dimensional shapes using parallel-jaw grippers, so $d=2$ and $m=2$.
In this work we also assume a finite width for each parallel jaw $w_j \in \mathbb{R}$.

Similar to~\cite{christopoulos2007handling}, we parameterize a grasp using a {\it line of action} for each gripper jaw, where each line of action is a 1D curve $\gamma(t): [0,1] \rightarrow \mathbb{R}^d$ with endpoints $\gamma(0) = \ba$ and $\gamma(1) = \bb$.
The line of action defines the trajectory that a jaw follows as the gripper closes around a shape.
A {\it grasp plan} is the set of lines of action for each of the jaws, $\Gamma = \{\gamma_1(\cdot),...,\gamma_m(\cdot)\})$ \cite{}.
For parallel-jaw grippers, $\Gamma = \{\gamma(t), \gamma(1 - t)\}$, since the two jaws approach the shape in opposite directions.
Furthermore, in this work we consider only straight lines of action.
The line of action model allows us to compute perturbations to the contact points and normals that occur due to shape uncertainty.
%We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changes in the location of contact with a surface, and the line of action allows us to compute these new locations.

Given a grasp plan and a deterministic shape, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following the given plan, $\bc_1, ..., \bc_m \in \mathbb{R}^d$.
We also refer to the unit outward pointing surface normals at the contact points as $\bn_1, ..., \bn_m \in \mathbb{R}^d$ and the object center of mass as $\bz \in \mathbb{R}^d$.
Together these form the set of grasp parameters $g = (\bc_1, ..., \bc_m, \bn_1, ... \bn_m, \bz)$ that enable us to evaluate the forces and torques that a given grasp can apply to an object.

%\begin{figure}[ht!]
%\centering
%\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
%\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
%\vspace*{-10pt}
%\label{fig:line_of_action}
%\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[width = 8cm, height = 6.5cm]{figures/grasp_model.jpg}
\caption{llustration of our grasping model for parallel jaw grippers on a GPIS model of a marker with shape uncertainty near the object center. Jaw placements are illustrated by a red direction arrow and line. The grasp plan consists of a line of action $\gamma(t)$ with endpoints $\ba$ and $\bb$. When following the grasp plan, the jaws contact the shape at locations $\bc_1$ and $\bc_2$ with outward pointing unit surface normals $\bn_1$ and $\bn_2$. Together with the center of mass of the object $\bz$, these values can be used to determine the forces and torques that a grasp can apply to an object. \todo{Jeff: Up to this point I don't believe the reader has seen a GPIS. We will replace the marker with a deterministic shape, but this figure gives a good idea of what we want to illustrate here.}}
\vspace*{-4ex}
\label{fig:grasp_model}
\end{figure}

\subsection{Sources of Uncertainty}
In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient.
Fig. \ref{fig:graphical_model} illustrates a graphical model of the relationship between these sources of uncertainty.
In this section we describe each source of uncertainty and our model of the uncertainty.
We wish to emphasize that the models of uncertainty described in this work are not the only models that may be used with MAB algorithms and that the reader may choose parameters and distributions that best fit their needs.

\subsubsection{Shape Uncertainty}

Uncertainty in object shape results from sensor noise and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015opt}.
Following ~\cite{laskey2015bandits, mahler2015opt} we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
A GPIS represents a distribution over signed distance functions (SDFs), a surface representation commonly used in 3D reconstruction and SLAM \cite{}.
An SDF is a real-valued function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
A GPIS is a gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ... \bx_n\}, \bx_i \in \mathbb{R}^d$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS.
See Appendix A for detail on how to train a mean and covariance function for a GPIS.
In this work, we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
For convenience, in later sections we will refer to the GPIS parameters as $\theta = \left( \mu_{f}(x), \Sigma_{f}(x) \right)$.

\todo{Jeff: Describe alternative representation of shape uncertainty that we run experiments on. Likely this will be Ben's polygonal model}

\subsubsection{Pose Uncertainty}
In typical robotics applications the pose of objects in the envinroment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
Therefore pose uncertainty may come from either a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
In practice this uncertainty may be quantified based on the algorithms used to register these frames to one another.
The effects of pose uncertainty on robotic grasping has been studied by~\cite{weisz2012pose, kim2012physically}. % cite Ben's RSS workshop paper here

In 2-dimensional space, the pose of an object $T$ is a member of the Lie Algebra $SE(2)$.
This matrix is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$:

\vspace{-2ex}
\begin{align*}
	T &= \left[  \begin{array}{ccc}
		\cos(\phi) & -\sin(\phi) & t_x \\
		\sin(\phi) & \cos(\phi) & t_y \\
		0 & 0 & 1
		\end{array} \right] .
\end{align*}

One challenge with pose is that the pose matrix $T$ is used to apply pose perturbations to an object in practice, but uncertainty is mathematically more easily quantified in terms of the pose parameters $\xi$.
Folowing Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$, and we define the pose random variable $T$ as

@@

\noindent where $\mathbf{\xi}^\wedge$ is the twist operator as defined in \cite{barfoot2014Pose}.

 \subsubsection{Motion Uncertainty}
In practice a robot may not be able to execute a desired grasp plan $\Gamma$ exactly due to slight errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
In this work, we model motion uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp plan $\Gamma$.
Formally, let $\hat{\by} = \frac{1}{2} (\ba + \bb)$ denote the center of a planned line of action $\gamma(t)$ and $\hat{\psi}$ denote the angle that the planned line $\bb - \ba$ makes with the x-axis of the 2D coordinate system on our shape representation.
Then the random center $\by \sim \mN(\hat{\by}, \Sigma_y)$ and the random angle $\psi \sim \mN(\hat{\psi}, \sigma_{\psi}^2)$.
For shorthand in the remainder of this paper we will refer to the random motion parameters as $\rho = \{\by, \psi \}$.
In practice $\Sigma_{y}^2$ and $\sigma_{\psi}^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.

 \subsubsection{Friction Uncertainty}
As shown in \cite{zheng2005}, uncertainty in friction coefficient can play a large role in grasp quality evaluation.
The expected friction coefficient $\hat{\mu}$ could be derived by means of object classification and a look up table~\cite{}.
However, friction coefficients may be uncertain due to factors such as material between a gripper and an object (e.g. dust, water, moisture), variations in the gripper material due to manufacturing tolerances, or misclassification of the object surface to be grasped.
We model uncertainty in friction coefficient as Gaussian noise, $\mu \sim \mN(\hat{\mu},\sigma_{\mu}^2)$.

\subsection{Grasp Quality}
We measure the quality of grassp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$, which we denote $P_F(\Gamma)$.
Force closure measures the ability to resist external wrenches, or force and torques vectors, assuming the grasp can apply infinite force.

Formally, force closure is a binary-valued quanity $F$ that is 1 if a grasp can resist wrenches in arbitrary directions and 0 otherwise.
Let $\mW \in \mathbb{R}^6$ denote the contact wrenches derived from contact locations $\bc_1, ... \bc_m$, normals $\bn_1, .., \bn_m$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
If the origin lies within the convex hull of $\mW$, then the grasp is in force closure\cite{}.
In this work we rank grasps using the probability of force closure given uncertainty in shape, pose, robot motion, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:
%\vspace{-2ex}
\begin{align*}
	P_F(\Gamma) &= P(F = 1 | \Gamma, \theta, \xi, \rho, \mu).
\end{align*}
\todo{Jeff: revise above symbols for clarity}
